A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-14 manuscript/manuscript.tex
Renamed *Selector to *Input

Selection criteria are specified by list of \emph{FilesetSelector} and
\emph{FieldSelector} objects provided to the \emph{inputs} argument of
the Study initialisation method. Matching is typically performed on file
names (dataset labels for XNAT repositories), and field names. If the
names are inconsistent across the study then regular expressions can be
used instead of exact matches by passing \emph{is\_regex=True} when
initialising the Selector. Additional criteria can be used to
distinguish cases where multiple filesets in the session match the
pattern provided, such as DICOM header values, or the order and ID
of the dataset.

>>>>

Selection criteria are specified by list of \emph{FilesetInput} and
\emph{FieldInput} objects provided to the \emph{inputs} argument of
the Study initialisation method. Matching is typically performed on file
names (dataset labels for XNAT repositories), and field names. If the
names are inconsistent across the study then regular expressions can be
used instead of exact matches by passing \emph{is\_regex=True} when
initialising the Selector. Additional criteria can be used to
distinguish cases where multiple filesets in the session match the
pattern provided, such as DICOM header values, or the order and ID
of the dataset.
